NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-12-05 RefereeReply1.txt

We would like to thank the referee for his/her constructive and valuable 
comments.  The points raised clearly helped us to further improve the 
quality of the manuscript.  Below we give detailed replies to the referee's 
queries and indicate the corresponding adjustments or additions to the 
manuscript.  We thereby follow the referee's initial ordering: 
1) 
2)
3)
4)
5)  We have somewhat improved the plots to better distinguish the 
    results with and without a jet veto. The caption of Fig. 4 is 
    amended accordingly. The focus, however, is on the ratios where 
    only a subset of results is plotted and legibility is, in our 
    estimation, sufficient for the points raised in the manuscript.
6)  As detailed in the manuscript in the paragraph above eq. (3.3), 
    we compute the LO result including its factorisation scale 
    uncertainty, and the EW correction factor for the central scale 
    choice. The NLO EW result, according to eq. (3.3) thus carries 
    the LO factorisation scale uncertainty.
    As labeled, the plots themselves show not delta-EW, which we compute only 
    for the central scale choice, but the full NLO EW result exhibiting 
    the LO factorisation scale uncertainty. In the ratios the NLO EW 
    result in relation to the central LO prediction is shown, i.e. 
    the resulting uncertainty band has the same relative size as 
    the LO uncertainty band.
    We have amended the caption of Fig. 4 to explicitly reflect 
    the reference of the ratio plots.
7)  We have rendered this statement more precise and hope that it 
    is clear now.
8)  The figure captions have been corrected.
9)  This has been rephrased to clearly state which particles the invariant 
    mass cut acts on.
10) The PDFs have been specified, and the respective publication referenced.
11) 
12) The description of the observables has been enhanced in the following 
    cases:
    - 
    - 
13) We agree and added a sentence stating exactly that.

### 2017-12-05 results.tex
corrected bib, added reply to 6) and 7)

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon 
    in triple photon production at the LHC at 13\,TeV. 
    The distributions are shown at LO (blue), NLO QCD (green), 
    NLO EW (orange), NLO \QCDpEW\ (black) and NLO \QCDtEW\ (red) 
    including scale uncertainties. The top panel displays the 
    absolute predictions for both the case with \revised{(dashed)} and without \revised{(solid)} the 
    application of a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$, 
    the latter ones are easily recognisable 
    due to their much reduced rate. The top ratio plot details 
    the relative corrections to the leading order cross section 
    without applying the jet veto, while the centre ratio plot 
    applies the jet veto. 
    The lower ratio highlights the size of the electroweak corrections.
    \label{fig:aaa:pt}
  }
\end{figure}

@@

The electroweak corrections, due to the absence of the opening 
of large new channels at the next-to-leading order, are dominated 
by the virtual corrections. 
Consequently, the release of the LO phase space restrictions 
in the real emission corrections only plays a minor role.
For all three photons the electroweak corrections are small but 
positive at small transverse momenta and exhibit the usual 
Sudakov shape at large transverse momenta.
They reach $-10\%$ for the leading and subleading photon and 
$-20\%$ for the third photon at $\pT=500\,\text{GeV}$. 
More importantly, beyond $\pT\gtrsim 170$, 140 and 80\,GeV 
for the first, second and third leading photon, respectively, 
the electroweak corrections are not covered by the LO 
uncertainty estimate.
Due to the different sizes of the QCD and electroweak 
corrections, the additive and multiplicative combination 
of corrections lead to very similar results.

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon 
    in triple photon production at the LHC at 13\,TeV. 
    The distributions are shown at LO (blue), NLO QCD (green), 
    NLO EW (orange), NLO \QCDpEW\ (black) and NLO \QCDtEW\ (red) 
    including scale uncertainties. The top panel displays the 
    absolute predictions for both the case with \revised{(dashed)} and without \revised{(solid)} the 
    application of a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$, 
    the latter ones are easily recognisable 
    due to their much reduced rate. The top ratio plot details 
    the relative corrections to the leading order cross section 
    without applying the jet veto, while the centre ratio plot 
    applies the jet veto. 
    The lower ratio highlights the size of the electroweak corrections.
    \revised{All ratios are taken with respect to the LO prediction 
    using out central scale choice.}
    \label{fig:aaa:pt}
  }
\end{figure}

@@

The electroweak corrections, due to the absence of the opening 
of large new channels at the next-to-leading order, are dominated 
by the virtual corrections. 
Consequently, the release of the LO phase space restrictions 
in the real emission corrections only plays a minor role.
For all three photons the electroweak corrections are small but 
positive at small transverse momenta and exhibit the usual 
Sudakov shape at large transverse momenta.
They reach $-10\%$ for the leading and subleading photon and 
$-20\%$ for the third photon at $\pT=500\,\text{GeV}$. 
More importantly, beyond $\pT\gtrsim 170$, 140 and 80\,GeV 
for the first, second and third leading photon, respectively, 
the electroweak corrections are not covered by the LO 
uncertainty estimate.
Due to the different sizes of QCD and electroweak 
corrections, \revised{$\deltaQCD\gg\deltaEW$,} the additive and multiplicative combination 
of corrections lead to very similar results 
\revised{as $\deltaQCD\deltaEW\ll\deltaQCD$}.
